### 2013-06-08 MSWL_ECO_lesson3.tex
Fix position of black box image
Revision chapter 3

    \item Advantages of public scrutiny and chances for improvements
    \begin{itemize}
        \item Compare benchmarks between projects and its goals. Could analyse every code line as you want and check every feature that has the product and compare with other projects using standar quality models\footnote{QSOS, OpenBRR, QUALOSS} adapted to your interests. And of course, anyone can view the source code of your project so you have to get it right and well documentated.
    \end{itemize}

    \item Real competition in development and maintenance
    \begin{itemize}
        \item In private projects there is only a main company that could develop improvements in software. Maintenance is very important and every new business model could grow around FLOSS projects. So your product as a costumer depends only of one company, what would happen if the company goes bankrupt?
    \end{itemize}

@@

\begin{itemize}
    \item \emph{Dependence on monopolies:}
    \begin{itemize}
        \item Real competition, better products, better services. The technology is not dependent on a single supplier, technology is the union of different suppliers in oneself when using the product, it can become a provider of the same technology.
    \end{itemize}  
    \item \emph{Importance of vendor reliability:}
    \begin{itemize}
        \item Future depends on product acceptance in the market. The vendor is exposed to continuous product analysis by different users. In every field of use of the product are certain tests that help the overall assessment and therefore the acceptance thereof by users. This process causes the provider to increase its reliability with regard to the consumer.
    \end{itemize}  
    \item \emph{Decisions taken based on few elements:}
    \begin{itemize}
        \item Software can be tested in its real environment, at a very low cost. You have the possibility to imagine all kind of test in every environment you choose to check product capabilities and compare your results with other analysis.
    \end{itemize}  
    \item \emph{Dependence on the strategy of providers:}
    \begin{itemize}
        \item Decisions on the evolution of a product taken for those contributing with resources. You have the possibility to include your thought into the product roadmap, also you can improve with your contributions to the project and share ideas with the community in an cross-ideas open platform.
    \end{itemize}  
    \item \emph{Confidence on "black boxes":}
    \begin{itemize}
        \item Using FLOSS projects we can see the whole process of the data inside de technology, we don't have \emph{black holes} where we miss which operations are done. We do not lose the path of process operations being applied to our data the software from input to output. For example an application service like gmail. This application hides we treat our data to drive the process of sending an email and the result shows that message has been sent as output  
    \end{itemize}  
    \begin{figure}[h]
        \begin{center}
            \includegraphics{blackbox}
            \caption[BlackBox]{BlackBox; we only can see the input and the output, not the process.}
            \label{fig:blackbox}
        \end{center}
    \end{figure}
\end{itemize}

@@

\textbf{TBC}

>>>>

    \item Advantages of public scrutiny and chances for improvements
    \begin{itemize}
        \item Compare benchmarks between projects and its goals. Could analyse every code line as you want and check every feature that has the product and compare with other projects using standard quality models\footnote{QSOS, OpenBRR, QUALOSS} adapted to your interests. And of course, anyone can view the source code of your project so you have to get it right and well documentated.
    \end{itemize}

    \item Real competition in development and maintenance
    \begin{itemize}
        \item In private projects there is only a main company that could develop improvements in software. Maintenance is very important and every new business model could grow around FLOSS projects. So your product as a costumer depends only on one company, what would happen if the company goes bankrupt?
    \end{itemize}

@@

\begin{itemize}
    \item \emph{Dependence on monopolies:}
    \begin{itemize}
        \item Real competition, better products, better services. The technology is not dependent on a single supplier, technology is the union of different suppliers in oneself when using the product, it can become a provider of the same technology.
    \end{itemize}  
    \item \emph{Importance of vendor reliability:}
    \begin{itemize}
        \item Future depends on product acceptance in the market. The vendor is exposed to continuous product analysis by different users. In every field of use of the product are certain tests that help the overall assessment and therefore the acceptance thereof by users. This process causes the provider to increase its reliability with regard to the consumer.
    \end{itemize}  
    \item \emph{Decisions taken based on few elements:}
    \begin{itemize}
        \item Software can be tested in its real environment, at a very low cost. You have the possibility to imagine all kind of test in every environment you choose to check product capabilities and compare your results with other analysis.
    \end{itemize}  
    \item \emph{Dependence on the strategy of providers:}
    \begin{itemize}
        \item Decisions on the evolution of a product taken for those contributing with resources. You have the possibility to include your thought into the product roadmap, also you can improve with your contributions to the project and share ideas with the community in an cross-ideas open platform.
    \end{itemize}  
    \item \emph{Confidence on "black boxes":}
    \begin{itemize}
        \item Using FLOSS projects we can see the whole process of the data inside de technology, we don't have \emph{black holes} where we miss which operations are done. We do not lose the path of process operations being applied to our data the software from input to output. For example an application service like gmail. This application hides we treat our data to drive the process of sending an email and the result shows that message has been sent as output
            \begin{figure}[htp]
                \begin{center}
                    \includegraphics{blackbox}
                    \caption[BlackBox]{BlackBox; we only can see the input and the output, not the process.}
                    \label{fig:blackbox}
                \end{center}
            \end{figure}

    \end{itemize}

\end{itemize}

\pagebreak

@@

Companies and public institutions would base its strategy on FLOSS because libre software is a viable business option, with high quality products, avoiding lock vendor, and technical reliability;  allows for new business opportunities, reducing barriers, incresing collaboration, and Libre software as an strategic tool; but it is important to know how to take advantage of those.

When in a business segment actors start to use free software, preventing in this niche monopolies or oligopolies and black boxes products, creating reliability products and available to test, and preventing dependency of strategies of providers.
